---
title: "ChickenData example into a ShinyApp"
author: "Andreia Carlos"
date: "18 October 2016"
output: html_document
---
        
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This ShinyApp presents tables with summary statistics of the Chicken's weight, for each diet. It is possible to filter the data by Time and compare the values in different times.


## Data processing

**Load required libraries**
```{r load libraries}
library(shiny)
library(dplyr)
library(tidyr)
```

**Process data into a format suitable for the shiny app**
```{r data processing}
Chick_print <- ChickWeight %>%
        select(weight, Time, Diet) %>%
        group_by(Diet, Time) %>%
        summarise( 
                N = n(),
                Mean = mean(weight),
                SD = sd(weight),
                Median = median(weight),
                Min = min(weight),
                Max = max(weight)
                ) %>%
        mutate( #Creating new variables merging the previous ones and giving it the right format
                pN = as.character(N), 
               pMeanSD = sprintf("%6.1f(%6.2f)", Mean, SD),
               pMedian = sprintf("%6.1f", Median),
               pMinMax = sprintf("%6.1f-%6.1f", Min, Max)
               ) %>%
        select(Diet, Time, N, pMeanSD, pMedian, pMinMax) %>% #select only the variables of interest
        gather("Statistics", "Value", 3:6) %>% #Get statistics into rows
        spread(Diet, Value, sep = ".") #Produce a dataset with diets in columns

```


## Developing the App

```{r define global variables}
Chick_base <- Chick_print
```

# Test 2

## Test with more than one table output

**1. Develop UI***
```{r ui}
ui <- fluidPage(
        titlePanel("Chicken Weight Data Summaries"),
        
         mainPanel(
                tabsetPanel(
                        tabPanel("All",
                                  dataTableOutput("Chick_print")),
                        tabPanel("Diet 1",
                                 dataTableOutput("Chick_print1")),
                        tabPanel("Diet 2",
                                 dataTableOutput("Chick_print2")),
                        tabPanel("Diet 3",
                                  dataTableOutput("Chick_print3")),
                        tabPanel("Diet 4",
                                  dataTableOutput("Chick_print4"))
                )
        ),
        # Create a new Row in the UI for selectInputs
        fluidRow(
                column(3,
                       selectInput("Time0",
                                   "Choose the baseline:",
                                   c("All",
                                     unique(as.character(Chick_base$Time))))
                ),
                uiOutput("Time1")
        ),
                # Create a new row for the table
        fluidRow(
                dataTableOutput("table")
        )
)
```

**2. Define a server App**
```{r App server}

server <- function(input, output){
        output$Time1 <- renderUI({
                if(input$Time0 != "All") {
                        column(3,
                       selectInput("Time1",
                                   "Select a Time for comparison:",
                                   c("All",
                                     unique(as.character(Chick_base$Time))))
                        )}
        })
        
        output$Chick_print <- renderDataTable({
                
                if(input$Time0 == "All") {
                        Chick_print <- Chick_base
                }
                else if(input$Time0 == input$Time1 | input$Time1 == "All") {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                }
               else {
                       Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                        Chick_print1 <- Chick_base[Chick_base$Time == input$Time1,]
                }
                Chick_print
                })
        
        output$Chick_print1 <- renderDataTable({
                
                if(input$Time0 == "All") {
                        Chick_print <- Chick_base
                }
                else if(input$Time0 == input$Time1 | input$Time1 == "All") {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                }
                else {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                        Chick_print1 <- Chick_base[Chick_base$Time == input$Time1,]
                        
                        Chick_print1 <- Chick_print %>%
                                left_join(Chick_print1, "Statistics") %>%
                                select(Statistics, Diet.1.x, Diet.1.y) 
                }
                Chick_print1
               
                })
         output$Chick_print2 <- renderDataTable({
                
                if(input$Time0 == "All") {
                        Chick_print <- Chick_base
                }
                else if(input$Time0 == input$Time1 | input$Time1 == "All" ) {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                }
                else {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                        Chick_print1 <- Chick_base[Chick_base$Time == input$Time1,]
                        
                        Chick_print2 <- Chick_print %>%
                                left_join(Chick_print1, "Statistics") %>%
                                select(Statistics, Diet.2.x, Diet.2.y)
 
                }
                Chick_print2
               
                })
         output$Chick_print3 <- renderDataTable({
                
                if(input$Time0 == "All") {
                        Chick_print <- Chick_base
                }
                else if(input$Time0 == input$Time1 | input$Time1 == "All" ) {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                }
                else {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                        Chick_print1 <- Chick_base[Chick_base$Time == input$Time1,]
                        
                        Chick_print3 <- Chick_print %>%
                                left_join(Chick_print1, "Statistics") %>%
                                select(Statistics, Diet.3.x, Diet.3.y)
                        
                }
                Chick_print3
               
                })
         output$Chick_print4 <- renderDataTable({
                
                if(input$Time0 == "All") {
                        Chick_print <- Chick_base
                }
                else if(input$Time0 == input$Time1 | input$Time1 == "All" ) {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                }
                else {
                        Chick_print <- Chick_base[Chick_base$Time == input$Time0,]
                        Chick_print1 <- Chick_base[Chick_base$Time == input$Time1,]
                        
                        Chick_print4 <- Chick_print %>%
                                left_join(Chick_print1, "Statistics") %>%
                                select(Statistics, Diet.4.x, Diet.4.y)
                        
                }
                Chick_print4
               
                })
        }

```

```{r data tables}
        Chick_print0 <- Chick_base[Chick_base$Time == 0,]
        Chick_print1 <- Chick_print %>%
                left_join(Chick_print0, "Statistics") %>%
                select(Statistics, Diet.1.x, Diet.1.y)
        Chick_print2 <- Chick_print %>%
                left_join(Chick_print0, "Statistics") %>%
                select(Statistics, Diet.2.x, Diet.2.y)
        Chick_print3 <- Chick_print %>%
                left_join(Chick_print0, "Statistics") %>%
                select(Statistics, Diet.3.x, Diet.3.y)
        Chick_print4 <- Chick_print %>%
                left_join(Chick_print0, "Statistics") %>%
                select(Statistics, Diet.4.x, Diet.4.y)
```

**3. Run the App**
```{r run}
shinyApp(server = server, ui = ui)
```
